The LSST-DESC 3x2pt Tomography Optimization Challenge

### 2021-08-27 paper/paper.tex
cite and acks
acks

ESC acknowledges support from the FAPESP (\#2019/19687-2) and CNPq  (\#308539/2018-4).
AHW is supported by a European Research Council Consolidator Grant (No. 770935). The work of EG and ABr was supported by the U.S. Department of Energy, Office of Science, Office of High Energy Physics Cosmic Frontier Research program under Award Number DE-SC0010008.

@@

>>>>

AHW is supported by a European Research Council Consolidator Grant (No. 770935).
The work of EG and ABr was supported by the U.S. Department of Energy, Office of Science, Office of High Energy Physics Cosmic Frontier Research program under Award Number DE-SC0010008.
CRB, ESC, BMOF, EJG, and GT made use of multi-GPU Sci-Mind Brunelleschi machines developed and tested for Artificial Intelligence and would like to thank CBPF Multi GPU development team of LITCOMP/COTEC, for supporting this infrastructure.
ESC acknowledges support from the FAPESP (\#2019/19687-2) and CNPq  (\#308539/2018-4).
MB acknowledges financial contributions from the agreement ASI/INAF 2018-23-HH.0, Euclid ESA mission - Phase D.
PH acknowledges generous support from the Hintze Family Charitable Foundation through the Oxford Hintze Centre for Astrophysical Surveys.

@@

For a further discussion of the merits of band triplets in machine learning photo-z see \citet{broussard_gawiser}
